Compact Core Galaxies in the RESOLVE Survey

### 2016-04-29 paperdraft.tex
new intro sections

CSSs have radii ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are also thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with a wealth of newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.

In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated dwarf elliptical galaxies (dE,Ns) are quite common, especially in clusters. \citet{Binggeli1991} find that of 225 dwarf galaxies present in the Virgo cluster, 174 are classfied as dEs or dE,Ns based on their sufrace brightness profiles. dEs and dE,Ns are also larger than CSSs with radii ranging from $\sim$600-800~pc \citep[e.g.,][]{Norris2014}, which may perhaps help their numbers. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Crawford2016}. They could also be the remnants of luminous compact blue dwarfs (LCBDs) that have been ram-pressure stripped and often quenched as they enter the cluster environment. There is also some evidence that dE,Ns are the progenitors of UCDs \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with radii up to 800~pc. The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios. Clues to how CCGs form may be given by their morphology i.e., one- or two-component structure, environments, star formation histories, and kinematics. We highlight these differences below.

%structure
The morphologies of \citet{Pfeffer2013} predict that tidally stripped remnants will display multi-component surface brightness profiles due to lingering outer galaxy structures. *** M32 has a bulge plus disk profile (Graham 2002)*** Dissipative processes could also cause cores to form as gas rushes to the center and star formation begins. *** Huxor cE has no underlying disk *** These effects could vary, however, based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.

%environments
CSSs have been found in a range of environments thus far. In the cluster environment we find UCDs \citep{Price2009,Madrid2010,Hasegan2005,Jones2006,Mieske2009,Wehner2007,Misgeld2008}, cEs \citep{Chilingarian2007,SmithCastelli2012,Price2009}, and dEs \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}. Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups. Lastly, only cEs have been found in isolated environments: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$ Mpc. CSSs found in group or cluster environments may be tidally stripped remnants, whereas isolated CCSs may rather be disippatively formed like normal Es.

*** include kicked out scenarios here ***

%colors

%kinematics
Another useful tool we have in discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$). \citet{Bender1992} and \citet{Bekki2003} show that $\sigma$ will remain largely unchanged when tidal stripping occurs, even though the \Reff\ and stellar mass will be greatly reduced. Thus, galaxies that are offset to higher $\sigma$ in a Faber-Jackson (stellar mass -- $\sigma$) relation \citep{faber1976} are most likely tidally stripped, while galaxies falling along the relation are most likely the low-mass extension of normal Es.

In this paper, we present a volume-limited sample of CCGs with key data quantifying their morphologies, environments, star formation histories, and kinematics. This paper is organized as follows. We describe our parent sample, the RESOLVE survey, in \autoref{resolve} and our comparison sample, the AIMSS catalog, in \autoref{aimss}. Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}. We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}. We next describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}. We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}. In \autoref{discussion}, we present a discussion of our results in the context of CCG formation and evolution. Lastly, the summary and future work are given in \autoref{conclusions}.

@@

\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs. RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages. RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \citet{York2000}), and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82. With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$. Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.

@@

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2016}). In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.

An important caveat to RESOLVE's completeness is that the survey is most likely to be missing the objects this study is focused on, cEs. This is because these objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}. We are engaged in ongoing efforts to use photo-z estimates to recover some of these objects.

@@

\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog (\citet{Norris2014}, \citet{Forbes2014}, \citet{Janz2015}) as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found in groups and clusters and includes both literature and newly discovered objects. Their process to find new CSSs is as follows. First, a search is conducted in the Hyperleda redshift catalog \citep{Paturel2003} for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$. Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies. Next, Source Extractor is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature. Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted. AIMSS also includes literature data for other UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.

@@

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}. The main differences in this processing are (1) improved sky subtraction following Blanton et al. (2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).

@@

The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al. in prep.). We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.

@@

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in \autoref{app}.

@@

\subsection{Environments}
\noindent We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}). We see many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could be at play. On the opposite end, we see several CCGs in massive group halos, and that these tend to be either core- or envelope dominated CCGs. This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies. There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.

\begin{figure*}[hbpt!]
\begin{center}
\includegraphics{nn_groupmass.eps}
\caption{We plot here the group halo mass against the nearest 3D neighbor for the RESOLVE survey and CCG sample. We see that CCGs live in a variety of environments, from extremely isolated (nearest neighbor $>$ 1 Mpc) to massive (M$_{\rm halo} \sim 10^{13}$ M$_{\odot}$) groups. There is no obvious trend into whether cores+envelopes and cores/envelopes preferentially live in different environments.}
\label{fig:envplot}
\end{center}
\end{figure*}

\subsection{Kinematics}
\label{kin}
\noindent We lastly investigate the kinematics of the CCG sample using the $\sigma$s derived from SOAR and Gemini telescope data. \autoref{fig:sigma} plots the $\sigma$-M$_{\star}$ relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with measured $\sigma$s. Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since  they will have more  Conversely, $\sigma$s that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.

We find that most of the CCGs tend to follow the dissipative formation track. However, there is one CCG with a core+envelope that lies close to M32, a tidally stripped cE, in the relation. We now take a closer look at this CCG, rf0492. This CCG lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}. Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$. This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.

@@

We now take an in depth look at the 8 CCGs with kinematics.

>>>>

CSSs have radii ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.

In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated counterparts (dE,Ns) are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. dEs are typically larger than CSSs with radii ranging up to $\sim800$~pc, whereas dE,Ns may have larger envelopes with a core radius <$800$~pc \citep[e.g.,][]{Norris2014}. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and often quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016}. There is also some evidence that dE,Ns are the progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with radii up to 800~pc. The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}, but have also been found near groups \citep{Crnojevi2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$~Mpc.

Environment bears on formation scenarios in different ways. One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CCSs may rather be dissipatively formed like Es. However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process. The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.

%structure
\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology. \citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin. \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures. Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center and star formation begins. This core is then ``puffed up'' through time as it interacts with other galaxies. The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation. It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.

Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found. \citet{Mastropietro2005a} use the N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not completely destroyed by ram pressure or tidal stripping. The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.

%colors
\textit{Star formation histories.} 
Colors and star formation rates are useful since they may point to recent star formation as a part of tidal stripping or dissipative formation. \citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations. \citet{Norris2011} find a similar result with one UCD best fit using older stellar populations. \citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.

%kinematics
\textit{Kinematics.}  The last useful tool we have for discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$). \citet{Bender1992} and \citet{Bekki2003} show that $\sigma$ will remain largely unchanged when tidal stripping occurs, even though the \Reff\ and stellar mass will be greatly reduced. Thus, galaxies that are offset to higher $\sigma$ in a Faber-Jackson (stellar mass -- $\sigma$) relation \citep{faber1976} are most likely tidally stripped, while galaxies falling along the relation are most likely the low-mass extension of normal Es.

In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey that have key data quantifying their morphologies, environments, star formation histories, and kinematics. We use this sample to examine the formation scenarios and evolution of CSSs and dEs/dE,Ns simultaneously as a spectrum of compact galaxies that span the gap from GCs to Es. Because we have derived a complete sample from RESOLVE, our sample contains CCGs at every evolutionary stage. This paper is organized as follows. We describe our parent sample, the RESOLVE survey, in \autoref{resolve} and our comparison sample, the AIMSS catalog, in \autoref{aimss}. Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}. We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}. We next describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}. We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}. In \autoref{discussion}, we present a discussion of our results in the context of CCG formation and evolution. Lastly, the summary and future work are given in \autoref{conclusions}.

@@

\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs. RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages. RESOLVE falls within the footprint of the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}, and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82. With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$. Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.

@@

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star}~\sim~10^{8.9}$~\Msun for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun in the B semester (see Figure 7 in \citet{Eckert2016}). In Figure 1, we plot the stellar masses against the deconvolved, one-component, half-light radius \Reff\ (see \autoref{deconv}) for all of RESOLVE along with the core-only \Reff\ for the CCG sample and see that these limits allow us to reach down to CSSs with sizes and masses similar to cEs.

An important caveat to RESOLVE's completeness is that the survey is preferentially incomplete for the very objects this study is focused on, cEs. Such round objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}. We are engaged in ongoing efforts to use photo-z estimates to recover some of these objects.

@@

\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both literature and newly discovered objects. Their process to find new CSSs is as follows. First, a search is conducted in the Hyperleda redshift catalog \citep{Paturel2003} for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$. Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies. Next, Source Extractor is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature. Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted. AIMSS also includes literature data for other UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.

@@

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}. The main differences in this processing are (1) improved sky subtraction following \citet{Blanton2011} for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method \citep[e.g., Figure 2 in][]{Eckert2015}.

@@

The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al., submitted). We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.

@@

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix.

@@

\subsection{Environments}
\noindent We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}). We see many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could be at play. On the opposite end, we see several CCGs in massive group halos, and that these tend to be either core- or envelope dominated CCGs. This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies. There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.

\begin{figure*}[hbpt!]
\begin{center}
\includegraphics{nn_groupmass_2d.eps}
\caption{We plot here the group halo mass against the nearest 3D neighbor for the RESOLVE survey and CCG sample. We see that CCGs live in a variety of environments, from extremely isolated (nearest neighbor $>$ 1 Mpc) to massive (M$_{\rm halo} \sim 10^{13}$ M$_{\odot}$) groups. There is no obvious trend into whether cores+envelopes and cores/envelopes preferentially live in different environments.}
\label{fig:envplot}
\end{center}
\end{figure*}

\subsection{Kinematics}
\label{kin}
\noindent We lastly investigate the kinematics of the CCG sample using the $\sigma$s derived from SOAR and Gemini telescope data. \autoref{fig:sigma} plots the $\sigma$-M$_{\star}$ relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with measured $\sigma$s. Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since  they will have more  Conversely, $\sigma$s that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies. Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.

@@

We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.

\subsection{rs0345}

\subsection{rs0567, rs1186, rf0078}

\subsection{rs1100}

\subsection{rf0003}

\subsection{rf0328}

\subsection{rf0492}
This galaxy has a core+envelope morphology and lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}. Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$. This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.7]{miniplots.eps}
\caption{Here we plot the stellar mass vs. velocity dispersion ($\sigma$) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog. Most CCGs appear to be following the dissipative formation track.}
\label{fig:miniplots}
\end{center}
\end{figure*}
